---
title: "Ch.3 Data Visualization"
author: "Jerri Schorr"
date: 09-24-2019
output: github_document
---
 
```{r setup chunk, include=FALSE}
library(tidyverse)
```

##### **Chapter 3**

###### **3.1**

* This chapter will cover ggplot
    + ggplot = __grammar of graphics__ 
    + uses a layering system
* Make sure to load the "tidyverse" package to use the ggplot functions

###### **3.2**

* I think that a smaller engine will get better gas milage, while a larger engine will get less gas mileage

```{r 3.2.1}
ggplot2::mpg
```

```{r 3.2.2}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```
    + This code proves that the original thought is true. As engine size increases, the gas milage decreases 
    
* The function "geom_point" creates the scatter plot layer to the graph
    + Here is a generic form of a ggplot:
    + ggplot(data = *DATA*) +  *GEOM_FUNCTION*(mapping = aes(*MAPPINGS*))
    
* Exercises
1. You get a blank white box
```{r 3.2.4}
ggplot(data = mpg)
```
4. Scatter plot of hwy vs. cyl
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = cyl, y = hwy))
  
```
5. Scatter plot of clas vs. drv
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = class, y = drv))
```


###### **3.3**

* Changing colors and shape

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = class))
```
```{r}
# Left
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, alpha = class))

# Right
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = class))
```
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```


###### **3.4**

* Common problems
    + Make sure to put a __+__ at the end of a line and not at the beginning

###### **3.5**

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
```

###### **3.6**

* **Geoms** are different geometric shapes used in the graph
    + bars, points, lines, ect.
    
```{r}
# left
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

# right
ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy))
```
    
###### **3.7**

* We will look at bar plots
    + Bars seem simple but have many things that go into creating them
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut))
```
    

###### **3.8**

* You can color bar chart using **colour** or **fill**
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, colour = cut))
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = cut))
```
* You can also fill with another variable
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = clarity))
```

* You can put bars next to each other with the **position** argument
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = clarity), position = "dodge")
```

###### **3.9**

*  You can flip the x and y axis with a quick function 

```{r}
ggplot(data = mpg, mapping = aes(x = class, y = hwy)) + 
  geom_boxplot()
ggplot(data = mpg, mapping = aes(x = class, y = hwy)) + 
  geom_boxplot() +
  coord_flip()
```

###### **3.10**

* Basic layering with ggplot

ggplot(data = *DATA*) + 
  *GEOM_FUNCTION*(
     mapping = aes(*MAPPINGS*),
     stat = *STAT*, 
     position = *POSITION*) +
  *COORDINATE_FUNCTION* +
  *FACET_FUNCTION*



